An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex
calibration example

\raft{FYI: Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
Indirect elicitation is a weaker condition than calibration~\citep{steinwart2008support,agarwal2015consistent,finocchiaro2021unifying}; we briefly sketch the argument.
Suppose $L$ is minimizable and $(L,\psi)$ is calibrated with respect to $\ell$, and set $\Gamma=\prop{L}$ and $\gamma=\prop{\ell}$.
Let $u\in\reals^d$ and $p\in\Gamma_u$.
From eq.~\eqref{eq:calibrated}, if $\psi(u) \notin \gamma(p)$, then we would have $u\notin\Gamma(p)$, a contradiction to $p\in\Gamma_u$.
Thus, $\psi(u) \in \gamma(p)$, so $p\in\gamma_{\psi(u)}$.
In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
\reviewerone{A}
\reviewerthree{A}
While this pair indirectly elicits the mode, we can show it is not calibrated with respect to $0-1$ loss. 
Suppose $ p  = (0, 1)$ and consider the sequence $\{1 - \frac 1 {n+1}\}_{n=1}^\infty$, which limits to $1$, but $\psi(u) = -1$ for all $u$ in the sequence.
Therefore, the infimum of hinge loss over reports not linking to $1$ approaches the infimum over all reports.
\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration, though their results generally do not apply to discrete prediction tasks.

>>>>

\raft{FYI: Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
Indirect elicitation is a weaker condition than calibration~\citep{steinwart2008support,agarwal2015consistent,finocchiaro2021unifying}; we briefly sketch the argument.
Suppose $L$ is minimizable and $(L,\psi)$ is calibrated with respect to $\ell$, and set $\Gamma=\prop{L}$ and $\gamma=\prop{\ell}$.
Let $u\in\reals^d$ and $p\in\Gamma_u$.
From eq.~\eqref{eq:calibrated}, if $\psi(u) \notin \gamma(p)$, then we would have $u\notin\Gamma(p)$, a contradiction to $p\in\Gamma_u$.
Thus, $\psi(u) \in \gamma(p)$, so $p\in\gamma_{\psi(u)}$.
In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
\reviewerone{A}
\reviewerthree{A}
While this pair indirectly elicits the mode, we can show it is not calibrated with respect to $0-1$ loss. 
Suppose $p = (0, 1) \in \simplex$ is the distribution putting all weight on $y=1$, and consider any sequence $u_n \to 1$ with $u_n < 1$ for all $n$.
Then the loss approaches the Bayes optimal, $L(1)_1 = 0$, but $\psi(u_n) = -1$ for all $n$, violating calibration.
\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration.

### 2023-06-15 poly-embed-journal/reviews/jmlr-response.tex
calibration example

	We have clarified this point with a concrete example; see margin comment A in orange.

@@

	The reviewer is correct on all the suggestions; we have made changes accordingly.
	See Comment B in orange for how we rephrased the sentence with too many parentheticals.

@@

\begin{itemize}
\item \textbf{Related work and discussion:}\\
 We thank the reviewer for the references and questions about the connections to $\mathcal{H}$-consistency and calibration. We have added a discussion about possible extensions to Section~\ref{sec:conclusion}. See margin comment A in blue.

@@

    We added footnote 7 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point. 
    See margin comment B.
    In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
    These questions appear challenging and heavily dependent on the setting (e.g.\ how costly data acquisition vs computation is).

@@

    We are not sure what the reviewer means by ``a Weston--Watkins polyhedral loss'', since we had thought of the Weston--Watkins hinge as a specific surrogate.
    But taking the question to mean ``is there a polyhedral surrogate consistent for 0--1 loss in multiclass settings?'', we added a brief discussion at the end of \S~\ref{sec:top-k} (``Surrogates for top-k classification'') giving such a hinge-like surrogate, a special case of the top-$k$ version with $k=1$.
    See margin comment C.

@@

    Yes, it does; in fact, we mention this fact informally following Construction 1; see margin comment D.

@@

	The choice of surrogate loss is of course important for consistency, but so is the choice of link function; see the discussion after Definition~\ref{def:indirect-elic}, marked by margin comment A in green.  
	(In particular, it seems the reviewer may be fixing the link to be the sign function; e.g. logistic loss is consistent with respect to 0-1 loss when using the sign link, but not with any other link.)

>>>>

	We have clarified this point with a concrete example; see margin note R1: A in orange.

@@

	The reviewer is correct on all the suggestions; we have made changes accordingly.
	See margin note R1: B in orange for how we rephrased the sentence with too many parentheticals.

@@

\begin{itemize}
\item \textbf{Related work and discussion:}\\
 We thank the reviewer for the references and questions about the connections to $\mathcal{H}$-consistency and calibration. We have added a discussion about possible extensions to Section~\ref{sec:conclusion}. See margin note R2: A in blue.

@@

    We added footnote 7 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point. 
    See margin note R2: B.
    In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
    These questions appear challenging and heavily dependent on the setting (e.g.\ how costly data acquisition vs computation is).

@@

    We are not sure what the reviewer means by ``a Weston--Watkins polyhedral loss'', since we had thought of the Weston--Watkins hinge as a specific surrogate.
    But taking the question to mean ``is there a polyhedral surrogate consistent for 0--1 loss in multiclass settings?'', we added a brief discussion at the end of \S~\ref{sec:top-k} (``Surrogates for top-k classification'') giving such a hinge-like surrogate, a special case of the top-$k$ version with $k=1$.
    See margin note R2: C.

@@

    Yes, it does.
    We mention this fact informally following Construction 1; see margin note R2: D.

@@

	The choice of surrogate loss is of course important for consistency, but so is the choice of link function; see the discussion after Definition~\ref{def:indirect-elic}, marked by margin note R3: A in green.  
	(In particular, it seems the reviewer may be fixing the link to be the sign function; e.g. logistic loss is consistent with respect to 0-1 loss when using the sign link, but not with any other link.)
